Specific Gene or Metabolite Levels

### 2025-05-14 RussoPaper/20250314_RussoManuscript_Fig1Revisions.Rmd
update

B = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Russo Fig 1 eclosion.csv")

@@

B.labels = c("w1118",
             "WT(LoxP)", "G85R(hr)",
             "WT(cr)", "G85R(cr)",
             "G85R(cr)/Sod1null", "WT(cr)/Sod1null", "Sod1null", 
             "A4V/A4V", "A4V/Sod1null","A4V/X16", "A4V/G85R(cr)")

@@

barplot(height = mean.B,
        ylim = c(0, 100),
        col = "black",
        las = 2,
        ylab = "Eclosion frequency (%)",
        main = "Eclosion from the pupal case",
        xaxt = "n")
axis(side = 1,
     at = c(.7 + (c(0:11)*1.2)),
     lwd = 3,
     line = 0,
     labels = B.labels,
     xpd = T,
     las = 2)
axis(side = 2,
     at = c(0,20,40,60,80,100),
     lwd = 3,
     line = 0,
     labels = F,
     xpd = T)
lines(x = c(-0.5,13.5),
     y = c(0,0),
     lwd = 3,
     xpd = T)

#abline(h = 100, lty = 2, lwd = 3)

@@

C.labels = c("w1118", "WT(CR)", "G85R", "A4V")

hex = function(color, alpha){
  rgbvals = col2rgb(color)
  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
  return(rgb2hex)
}

@@

boxplot(C$Boutons~C$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(0, 150),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = c(hex("navy", .25),
                hex("skyblue", .25),
                hex('orange', .25),
                hex("deeppink", .25)),
        add = T, 
        xaxt = "n",
        frame = F)

points(x=as.numeric(C$x),
       y=C$Boutons,
       cex=2.25,
       pch=21,
       bg=c('navy',"skyblue", 'orange', "deeppink")[as.numeric(C$Genotype)])

@@

D.labels = c("w1118", "WTLoxP", "G85R(HR)", "WT(CR)", "G85R", "A4V")

@@

boxplot(D$Boutons~D$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(0, 150),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = c(hex("navy", .25),
                hex("gold2", .25),
                hex("turquoise4", .25),
                hex("skyblue", .25),
                hex('orange', .25),
                hex("deeppink", .25)),
        add = T, 
        xaxt = "n",
        frame = F)

points(x=as.numeric(D$x),
       y=D$Boutons,
       cex=2.25,
       pch=21,
       bg=c('navy', "gold2", "turquoise4", 
            "skyblue", 'orange', "deeppink")[as.numeric(D$Genotype)])

@@

E.labels = c("w1118", "WTLoxP", "G85R(HR)", 
             "WT(CR)", "G85R", "A4V",
             "A4V/X16", "A4V/G85R")

@@

bar.colors = c(hex("navy", .75),
                hex("gold2", .75),
                hex("turquoise4", .75),
                hex("skyblue", .75),
                hex('orange', .75),
                hex("deeppink", .75),
                hex('grey', .75),
                hex("darkgreen", .75))

border.colors = c('navy', "gold2", "turquoise4",
                  "skyblue", 'orange', "deeppink", 
                  "grey", "green4")

@@

text(x = tick.x[3],
     y = (mean.E[3] + stderr.E[3]) + 5,
    labels = "*",
    cex = 2)

@@

>>>>

library(kableExtra)

std.colors = setNames(c('navy', "gold2", "turquoise4", "royalblue",
                        'orange', "deeppink", "grey", "green4"),
                      c("w1118", "WT(LoxP)", "G85R(hr)", "WT(cr)",
                        "G85R(cr)", "A4V", "A4V/X16", "A4V/G85R(cr)"))

hex = function(color, alpha){
  rgb2hex = color
  i = 1
  while(i <= length(color)){
    rgbvals = col2rgb(color[i])
    rgb2hex[i] = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
    i = i+1
  }
  return(rgb2hex)
}

B = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Russo Fig 1 eclosion.csv")
B.labels = c("w1118",
             "WT(LoxP)", "G85R(hr)",
             "WT(cr)", "G85R(cr)",
             "G85R(cr)/Sod1null", "WT(cr)/Sod1null", "Sod1null", 
             "A4V", "A4V/Sod1null","A4V/X16", "A4V/G85R(cr)")

colnames(B) = B.labels

@@

@@

barplot(height = mean.B,
        ylim = c(0, 120),
        col = "black",
        las = 2,
        ylab = "Eclosion frequency (%)",
        main = "Eclosion from the pupal case",
        xaxt = "n",
        yaxt = "n")
axis(side = 1,
     at = c(.7 + (c(0:11)*1.2)),
     lwd = 3,
     line = 0,
     labels = B.labels,
     xpd = T,
     las = 2)
axis(side = 2,
     at = c(0,20,40,60,80,100),
     lwd = 3,
     line = 0,
     labels = T,
     xpd = T,
     las = 2)

lines(x = c(-0.5,13.5),
     y = c(0,0),
     lwd = 3,
     xpd = T)

lines(x = c(1.9,3.1),
      y = c(105, 105),
      lwd = 3)

lines(x = c(1.9,1.9),
      y = c(105, 102),
      lwd = 3)
lines(x = c(3.1, 3.1),
      y = c(105, 40),
      lwd = 3)

text(x = 3.1,
     y = 109,
    labels = "*",
    cex = 2)

lines(x = c(4.3,9.1),
      y = c(105, 105),
      lwd = 3)

lines(x = c(4.3,4.3),
      y = c(105, 102),
      lwd = 3)
lines(x = c(5.5, 5.5),
      y = c(105, 40),
      lwd = 3)
lines(x = c(6.7, 6.7),
      y = c(105, 95),
      lwd = 3)
lines(x = c(9.1, 9.1),
      y = c(105, 95),
      lwd = 3)

text(x = 5.5,
     y = 109,
    labels = "*",
    cex = 2)

lines(x = c(5.5,11.5),
      y = c(116, 116),
      lwd = 3)

lines(x = c(5.5, 5.5),
      y = c(116, 113),
      lwd = 3)
lines(x = c(10.3, 10.3),
      y = c(116, 100),
      lwd = 3)
lines(x = c(11.5, 11.5),
      y = c(116, 102),
      lwd = 3)

text(x = 10.3,
     y = 120,
    labels = "*",
    cex = 2,
    xpd = t)

```{r echo = F, include = F}

#B.data = data.frame(Genotype = rep(B.labels[1], length(na.omit(B[,1]))),
#                    Eclosion = na.omit(B[,1]))

#i = 1
#while(i <= ncol(B)){
#  temp.B = data.frame(Genotype = rep(B.labels[i], length(na.omit(B[,i]))),
#                      Eclosion = na.omit(B[,i]))
#  B.data = rbind(B.data, temp.B)
#  i = i+1
#}

#B.aov = aov(B.data$Eclosion~B.data$Genotype)

#head(summary(B.aov))

#head(TukeyHSD(B.aov))

t.table = data.frame(Genotype1 = B.labels[1],
                     Genotype2 = B.labels[2],
                     pval = t.test(x = na.omit(B[,1]),
                                   y = na.omit(B[,2]),
                                   paired = F)[[3]])

i=1
while(i <= ncol(B)){
  j = i+1
  while(j <= ncol(B)){
    if(length(unique(na.omit(B[,i]))) == 1 &
       length(unique(na.omit(B[,j]))) == 1){
      t.temp = data.frame(Genotype1 = B.labels[i],
                          Genotype2 = B.labels[j],
                          pval = 0)
      j = j+1
    }

    if(!(length(unique(na.omit(B[,i]))) == 1 &
         length(unique(na.omit(B[,j]))) == 1)){
      t.temp = data.frame(Genotype1 = B.labels[i],
                          Genotype2 = B.labels[j],
                          pval = t.test(x = na.omit(B[,i]),
                                        y = na.omit(B[,j]),
                                        paired = F)[[3]])
      t.table = rbind(t.table, t.temp)
      j = j+1
    }
  }
  i = i+1
}

t.stripe = t.table$pval <= .05
#row.names(t.table) = c(1:nrow(t.table))

knitr::kable(t.table,
             caption = 'All t-tests for figure 1B eclosion data.')  %>%
kable_styling() %>%
row_spec(c(1:nrow(t.table))[t.table$pval <= .05], bold = T, color = "black", background = "gold")

target.pvals = t.table[c(13, 30, 34, 38, 40, 55, 59),]

knitr::kable(target.pvals,
             caption = 'All t-tests for figure 1B eclosion data.')  %>%
kable_styling() %>%
row_spec(c(1:nrow(target.pvals))[target.pvals$pval <= .05], bold = T, color = "black", background = "gold")

@@

C.labels = c("w1118", "WT(cr)", "G85R(cr)", "A4V")
C.cols = std.colors[C.labels]

@@

boxplot(C$Boutons~C$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(0, 150),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = hex(C.cols, .25),
        add = T, 
        xaxt = "n",
        frame = F)

points(x=as.numeric(C$x),
       y=C$Boutons,
       cex=2.25,
       pch=21,
       bg=C.cols[C$Genotype])

@@

D.labels = c("w1118", "WT(LoxP)", "G85R(hr)", "WT(cr)", "G85R(cr)", "A4V")

D.cols = std.colors[D.labels]

@@

boxplot(D$Boutons~D$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(0, 150),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = hex(D.cols, .25),
        add = T, 
        xaxt = "n",
        frame = F)

points(x=as.numeric(D$x),
       y=D$Boutons,
       cex=2.25,
       pch=21,
       bg=D.cols[D$Genotype])

@@

E.labels = c("w1118", "WT(LoxP)", "G85R(hr)", "WT(cr)", "G85R(cr)", 
             "A4V", "A4V/X16", "A4V/G85R(cr)")

E.cols = std.colors[E.labels]

@@

bar.colors = hex(E.cols, .75)

border.colors = E.cols

@@

lines(x = c(1.9,3.1),
      y = c(63, 63),
      lwd = 3)

text(x = 2.5,
     y = 66,
    labels = "*",
    cex = 2,
    xpd = t)

@@

colnames(E) = E.labels

t.fE = data.frame(Sample1 = E.labels[2],
                  Sample2 = E.labels[3],
                  pval = t.test(x = E[, E.labels[2]],
                                  y = E[, E.labels[3]],
                                  paired = F)[[3]])

temp.t.fE = data.frame(Sample1 = E.labels[4],
                       Sample2 = E.labels[5],
                       pval = t.test(x = E[, E.labels[4]],
                                     y = E[, E.labels[5]],
                                     paired = F)[[3]])
t.fE = rbind(t.fE, temp.t.fE)

temp.t.fE = data.frame(Sample1 = E.labels[4],
                       Sample2 = E.labels[6],
                       pval = t.test(x = E[, E.labels[4]],
                                     y = E[, E.labels[6]],
                                     paired = F)[[3]])
t.fE = rbind(t.fE, temp.t.fE)

knitr::kable(t.fE,
             caption = 'All t-tests for figure 1E larval locomotion data.')  %>%
kable_styling() %>%
row_spec(c(1:nrow(t.fE))[t.fE$pval <= .05], bold = T, color = "black", background = "gold")

```{r include = F, echo = F, include = F}

fig2ab = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Figure 2AB.csv", header = T)
fig2ab$Sample = paste(fig2ab$Genotype, paste(fig2ab$Sex, fig2ab$Day))

fig2ab$Genotype[fig2ab$Genotype == "dSodWT"] = "WT(cr)"

```{r echo = F, fig.width=7.5}

f.fig2ab = fig2ab[fig2ab$Sex == 'F' &
                 (fig2ab$Day == 3 |
                  fig2ab$Day == 14 |
                  fig2ab$Day == 20 |
                  fig2ab$Day == 28 |
                  fig2ab$Day == 35) &
                  fig2ab$Genotype != 'w1118',]

f.fig2ab = f.fig2ab[order(fig2ab$Day),]
f.fig2ab$Sample = paste(f.fig2ab$Genotype, f.fig2ab$Day)
f.fig2ab$Sample = factor(f.fig2ab$Sample, levels = c('WT(cr) 3', 'A4V 3',
                                                     'WT(cr) 14', 'A4V 14',
                                                     'WT(cr) 20', 'A4V 20',
                                                     'WT(cr) 28', 'A4V 28',
                                                     'WT(cr) 35', 'A4V 35'))
f.fig2ab = na.omit(f.fig2ab)
f.fig2ab$x = as.numeric(f.fig2ab$Sample)

##put space between time points
f.fig2ab$x[f.fig2ab$x > 8] = f.fig2ab$x[f.fig2ab$x > 8] + 1
f.fig2ab$x[f.fig2ab$x > 6] = f.fig2ab$x[f.fig2ab$x > 6] + 1
f.fig2ab$x[f.fig2ab$x > 4] = f.fig2ab$x[f.fig2ab$x > 4] + 1
f.fig2ab$x[f.fig2ab$x > 2] = f.fig2ab$x[f.fig2ab$x > 2] + 1

f2ab.cols = std.colors[c("WT(cr)", "A4V")]

f.fig2ab$color = std.colors[f.fig2ab$Genotype]

f.fig2ab = f.fig2ab[order(f.fig2ab$Rate),]
f.fig2ab = f.fig2ab[order(f.fig2ab$Sample),]
f.fig2ab$x.adj = rep(c(-.25, .25 ,0), 20)
f.fig2ab$x.adj = c(0, -.25, .25, -.15, .15, 0,
                   0, -.15, .15, -.15, .15, 0,

                   0, 0, .2, -.2, 0, 0,
                   -.15, .15, 0, 0, -.15, .15,

                   0, 0, -.15, .15, 0, 0,
                   0, 0, -.25, .25, 0, 0,

                   0, -.25, .25, 0, 0, 0,
                   -.15, .15, 0, 0, 0, 0,

                   0, -.25, .25, -.15, .15, 0,
                   -.25, .25, 0, -.25, .25, 0)

f.fig2ab$x = f.fig2ab$x + f.fig2ab$x.adj

par(mar=c(5.1, 4.1, 4.1, 5.6))

boxplot(f.fig2ab$Rate~f.fig2ab$Sample,
        at = c(1,2, 4,5, 7,8, 10,11, 13,14),
        xaxt = 'none',
        xlab = "Day",
        col = hex(f2ab.cols, .25),
        ylab = 'Veloxicty (cm/sec)',
        main = "Female Climbing Velocity",
        ylim = c(0,2))
points(x = f.fig2ab$x,
       y = f.fig2ab$Rate,
       pch = 21,
       bg = f.fig2ab$color)
axis(side = 1,
     at = c(1.5, 4.5, 7.5, 10.5, 13.5),
     labels = c(3, 14, 20, 28, 35))

legend('topright',
       inset=c(-0.185,0),
       legend = c('WT(cr)', 'A4V'), 
       fill = f2ab.cols,
       cex = 1,
       bty = 'n',
       pt.cex = .5,
       xpd = T)

lines(x = c(1,2),
      y = c(1.6, 1.6),
      lwd = 1.5)

text(x = 1.5,
     y = 1.7,
    labels = "*",
    cex = 1.5,
    xpd = t)

lines(x = c(10,11),
      y = c(1.4, 1.4),
      lwd = 1.5)

text(x = 10.5,
     y = 1.5,
    labels = "*",
    cex = 1.5,
    xpd = t)

lines(x = c(13,14),
      y = c(1.0, 1.0),
      lwd = 1.5)

text(x = 13.5,
     y = 1.1,
    labels = "*",
    cex = 1.5,
    xpd = t)

f2ab.labels = unique(f.fig2ab$Sample)
t.f2ab = data.frame(Sample1 = f2ab.labels[1],
                    Sample2 = f2ab.labels[2],
                    pval = t.test(x = f.fig2ab[f.fig2ab$Sample == f2ab.labels[1], "Rate"],
                                  y = f.fig2ab[f.fig2ab$Sample == f2ab.labels[2], "Rate"],
                                  paired = F)[[3]])

i=3
while(i<=length(unique(f.fig2ab$Sample))){
  temp = data.frame(Sample1 = f2ab.labels[i],
                    Sample2 = f2ab.labels[i+1],
                    pval = t.test(x = f.fig2ab[f.fig2ab$Sample == f2ab.labels[i], "Rate"],
                                  y = f.fig2ab[f.fig2ab$Sample == f2ab.labels[i+1], "Rate"],
                                  paired = F)[[3]])
  t.f2ab = rbind(t.f2ab, temp)
  i=i+2
}

knitr::kable(t.f2ab,
             caption = 'All t-tests for figure 2a climbing data.')  %>%
kable_styling() %>%
row_spec(c(1:nrow(t.f2ab))[t.f2ab$pval <= .05], bold = T, color = "black", background = "gold")

```{r echo = F, fig.width=7.5}

m.fig2ab = fig2ab[fig2ab$Sex == 'M' &
                 (fig2ab$Day == 3 |
                  fig2ab$Day == 7 |
                  fig2ab$Day == 12 |
                  fig2ab$Day == 16) &
                  fig2ab$Genotype != 'w1118',]

m.fig2ab = m.fig2ab[order(fig2ab$Day),]
m.fig2ab$Sample = paste(m.fig2ab$Genotype, m.fig2ab$Day)
m.fig2ab$Sample = factor(m.fig2ab$Sample, levels = c('WT(cr) 3', 'A4V 3',
                                                     'WT(cr) 7', 'A4V 7',
                                                     'WT(cr) 12', 'A4V 12',
                                                     'WT(cr) 16', 'A4V 16'))
m.fig2ab = na.omit(m.fig2ab)
m.fig2ab$x = as.numeric(m.fig2ab$Sample)
m.fig2ab$x[m.fig2ab$x > 6] = m.fig2ab$x[m.fig2ab$x > 6] + 1
m.fig2ab$x[m.fig2ab$x > 4] = m.fig2ab$x[m.fig2ab$x > 4] + 1
m.fig2ab$x[m.fig2ab$x > 2] = m.fig2ab$x[m.fig2ab$x > 2] + 1

m2ab.cols = std.colors[c("WT(cr)", "A4V")]

m.fig2ab$color = std.colors[m.fig2ab$Genotype]

m.fig2ab = m.fig2ab[order(m.fig2ab$Rate),]
m.fig2ab = m.fig2ab[order(m.fig2ab$Sample),]
m.fig2ab$x.adj = rep(c(-.25, .25 ,0), 16)
m.fig2ab$x.adj = c(0, -.25, .25, 0, -.1, .1,
                   0, -.25, .25, .0, -.1, .1,

                   0, 0, -.1, .1, 0, 0,
                   0, -.1, .1, 0, 0, 0,

                   0, -.1, .1, 0, 0, 0,
                   0, -.1, .1, 0, -.1, .1,

                   0, -.25, 0, .25, .15, 0,
                   0, -.25, 0, .25, -.15, .15)

m.fig2ab$x = m.fig2ab$x + m.fig2ab$x.adj

par(mar=c(5.1, 4.1, 4.1, 5.6))

boxplot(m.fig2ab$Rate~m.fig2ab$Sample,
        at = c(1,2, 4,5, 7,8, 10,11),
        xaxt = 'none',
        xlab = "Day",
        col = hex(m2ab.cols, .25),
        ylab = 'Veloxicty (cm/sec)',
        main = "Male Climbing Velocity",
        ylim = c(0,3))
points(x = m.fig2ab$x,
       y = m.fig2ab$Rate,
       pch = 21,
       bg = m.fig2ab$color)
axis(side = 1,
     at = c(1.5, 4.5, 7.5, 10.5),
     labels = c(3, 7, 12, 16))

legend('topright',
       inset=c(-0.185,0),
       legend = c('WT(cr)', 'A4V'), 
       fill = m2ab.cols,
       cex = 1,
       bty = 'n',
       pt.cex = .5,
       xpd = T)

lines(x = c(7,8),
      y = c(2.7, 2.7),
      lwd = 1.5)

text(x = 7.5,
     y = 2.8,
    labels = "*",
    cex = 1.5,
    xpd = t)

lines(x = c(10,11),
      y = c(2.2, 2.2),
      lwd = 1.5)

text(x = 10.5,
     y = 2.3,
    labels = "*",
    cex = 1.5,
    xpd = t)

m2ab.labels = unique(m.fig2ab$Sample)
t.m2ab = data.frame(Sample1 = m2ab.labels[1],
                    Sample2 = m2ab.labels[2],
                    pval = t.test(x = m.fig2ab[m.fig2ab$Sample == m2ab.labels[1], "Rate"],
                                  y = m.fig2ab[m.fig2ab$Sample == m2ab.labels[2], "Rate"],
                                  paired = F)[[3]])

i=3
while(i<=length(unique(m.fig2ab$Sample))){
  temp = data.frame(Sample1 = m2ab.labels[i],
                    Sample2 = m2ab.labels[i+1],
                    pval = t.test(x = m.fig2ab[m.fig2ab$Sample == m2ab.labels[i], "Rate"],
                                  y = m.fig2ab[m.fig2ab$Sample == m2ab.labels[i+1], "Rate"],
                                  paired = F)[[3]])
  t.m2ab = rbind(t.m2ab, temp)
  i=i+2
}

knitr::kable(t.m2ab,
             caption = 'All t-tests for figure 2b climbing data.')  %>%
kable_styling() %>%
row_spec(c(1:nrow(t.m2ab))[t.m2ab$pval <= .05], bold = T, color = "black", background = "gold")

Aleah.1 = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Aleah G85R Pharate Sex Ratio Data.csv")

mean.aleah1 = setNames(c(mean(Aleah.1$PercentM), mean(Aleah.1$PercentF), mean(Aleah.1$PercentU)),
                       c("Male", "Female", "Indeterminate"))
stderr.aleah1 = setNames(c(sd(Aleah.1$PercentM)/(sqrt(11)),
                           sd(Aleah.1$PercentF)/(sqrt(11)),
                           sd(Aleah.1$PercentU)/(sqrt(11))),
                       c("Male", "Female", "Indeterminate"))

barplot(height = mean.aleah1,
        ylim = c(0, 100),
        col = c("royalblue", "deeppink", "grey40"),
        las = 1,
        ylab = "Percent Total Pharates",
        main = "G85R Pharate Sex Ratio",
        border = "black")

axis(side = 2,
     at = c(0,20,40,60,80,100),
     lwd = 3,
     line = 0,
     labels = T,
     las = 2,
     xpd = T)

lines(x = c(0,3.75),
     y = c(0,0),
     lwd = 3,
     xpd = T)

i = 1
while(i <= length(stderr.aleah1)){
  lines(x = tick.x[c(i,i)],
        y = c(mean.aleah1[i], (mean.aleah1[i] + stderr.aleah1[i])),
        lwd = 3,
        col = "black")

  lines(x = c((tick.x[i] - .25), (tick.x[i] + .25)),
        y = c((mean.aleah1[i] + stderr.aleah1[i]), (mean.aleah1[i] + stderr.aleah1[i])),
        lwd = 3,
        col = "black")

sum.aleah1 = setNames(c(sum(Aleah.1$Male), sum(Aleah.1$Female), sum(Aleah.1$Undetermined)),
                      c("Males", "Females", "Indeterminate"))

pie(sum.aleah1,
    labels = c(paste0(names(mean.aleah1), " (", signif(mean.aleah1, 3), "%)")),
    init.angle = -90,
    col = c("royalblue", "deeppink", "grey60"),
    edges = 300,
    border = T,
    lwd = 5)
legend('topright',
       inset=c(0,0),
       legend = names(mean.aleah1), 
       fill = c("royalblue", "deeppink", "grey60"),
       cex = 1,
       bty = 'n',
       pt.cex = .5,
       xpd = T)

Aleah.2 = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Aleah G85R Larvae Sex Ratio Data.csv")

mean.aleah2 = setNames(c(mean(na.omit(Aleah.2$G85R.M)), 
                         mean(na.omit(Aleah.2$G85R.F)),
                         mean(na.omit(Aleah.2$WT.M)), 
                         mean(na.omit(Aleah.2$WT.F))),
                       c("G85R Male", "G85R Female", "WT Male", "WT Female"))
stderr.aleah2 = setNames(c(sd(na.omit(Aleah.2[,1]))/(length(na.omit(Aleah.2[,1]))),
                           sd(na.omit(Aleah.2[,2]))/(length(na.omit(Aleah.2[,2]))),
                           sd(na.omit(Aleah.2[,3]))/(length(na.omit(Aleah.2[,3]))),
                           sd(na.omit(Aleah.2[,4]))/(length(na.omit(Aleah.2[,4])))),
                         c("G85R Male", "G85R Female", "WT Male", "WT Female"))

tick.x = c(1, 2.15, 3.9, 5.05)

par(mar = c(4,4,4,2), lwd = 3)

barplot(height = mean.aleah2,
        ylim = c(0, 55),
        col = c("royalblue", "deeppink", "royalblue", "deeppink"),
        las = 1,
        ylab = "Number of larvae",
        main = "dSod1 third instar sex ratio",
        border = "black",
        xaxt = "n",
        space = c(.5,.15,.75,.15))
axis(side = 2,
     at = c(0,10,20,30,40,50),
     lwd = 3,
     line = 0,
     labels = T,
     las = 2,
     xpd = T)

axis(side = 1,
     at = c(1, 2.15, 3.9, 5.05),
     lwd = 3,
     line = 0,
     labels = F,
     las = 1,
     xpd = T)

axis(side = 1,
     at = tick.x,
     lwd = 0,
     line = -0.25,
     labels = c("Male", "Female", "Male", "Female"),
     las = 1,
     xpd = T)

axis(side = 1,
     at = c(1.55, 4.5),
     lwd = 0,
     line = .75,
     labels = c("G85R", "WT"),
     las = 1,
     xpd = T)

lines(x = c(0.25, 5.75),
     y = c(0,0),
     lwd = 3,
     xpd = T)

i = 1
while(i <= length(stderr.aleah2)){
  lines(x = tick.x[c(i,i)],
        y = c(mean.aleah2[i], (mean.aleah2[i] + stderr.aleah2[i])),
        lwd = 3,
        col = "black")

  lines(x = c((tick.x[i] - .25), (tick.x[i] + .25)),
        y = c((mean.aleah2[i] + stderr.aleah2[i]), (mean.aleah2[i] + stderr.aleah2[i])),
        lwd = 3,
        col = "black")

lines(x = c(1,2.15),
      y = c(22, 22),
      lwd = 2)

text(x = 1.575,
     y = 25,
    labels = "ns",
    cex = 1.5,
    xpd = t)

lines(x = c(3.9,5.05),
      y = c(49, 49),
      lwd = 2)

text(x = 4.4525,
     y = 52,
    labels = "ns",
    cex = 1.5,
    xpd = t)

t.Aleah2 = data.frame(Sample1 = c("G85R.Males", "WT.Males"),
                      Sample2 = c("G85R.Females", "WT.Females"),
                      pval = c(t.test(x = na.omit(Aleah.2$G85R.M),
                                      y = na.omit(Aleah.2$G85R.F),
                                      paired = F)[[3]],
                               t.test(x = na.omit(Aleah.2$WT.M),
                                    y = na.omit(Aleah.2$WT.F),
                                    paired = F)[[3]]))

knitr::kable(t.Aleah2,
             caption = "All t-tests for Aleah's larval sex ratio data.")  %>%
kable_styling() %>%
row_spec(c(1:nrow(t.Aleah2))[t.Aleah2$pval <= .05], bold = T, color = "black", background = "gold")

gbbEcl = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Ana_gbbEclosionData.csv")

gbbEcl.labels = unique(gbbEcl$Genotype)

gbbEcl.means = rep(0, length(gbbEcl.labels))

i = 1
while(i<=length(gbbEcl.labels)){
  gbbEcl.means[i] = mean(gbbEcl$PercentEclosion[gbbEcl$Genotype == gbbEcl.labels[i]])
  i = i+1
}

stderr.gbbEcl = setNames(c(sd(gbbEcl[gbbEcl==gbbEcl.labels[1],"PercentEclosion"])/4,
                           sd(gbbEcl[gbbEcl==gbbEcl.labels[2],"PercentEclosion"])/4,
                           sd(gbbEcl[gbbEcl==gbbEcl.labels[3],"PercentEclosion"])/4,
                           sd(gbbEcl[gbbEcl==gbbEcl.labels[4],"PercentEclosion"])/4,
                           sd(gbbEcl[gbbEcl==gbbEcl.labels[5],"PercentEclosion"])/4,
                           sd(gbbEcl[gbbEcl==gbbEcl.labels[6],"PercentEclosion"])/4),
                         gbbEcl.labels)

par(mar = c(12,4,4,2))

barplot(height = gbbEcl.means,
        ylim = c(0, 120),
        col = "black",
        las = 2,
        ylab = "Eclosion frequency (%)",
        main = "Eclosion from the pupal case",
        xaxt = "n",
        yaxt = "n")
axis(side = 1,
     at = c(.7 + (c(0:5)*1.2)),
     lwd = 3,
     line = 0,
     labels = gbbEcl.labels,
     xpd = T,
     las = 2)
axis(side = 2,
     at = c(0,20,40,60,80,100),
     lwd = 3,
     line = 0,
     labels = T,
     xpd = T,
     las = 2)

tick.x = c(.7 + (c(0:5)*1.2))

i = 1
while(i <= length(stderr.gbbEcl)){
  if(stderr.gbbEcl[i] > 0){
    lines(x = tick.x[c(i,i)],
          y = c(gbbEcl.means[i], (gbbEcl.means[i] + stderr.gbbEcl[i])),
          lwd = 3,
          col = "black")

    lines(x = c((tick.x[i] - .25), (tick.x[i] + .25)),
          y = c((gbbEcl.means[i] + stderr.gbbEcl[i]), (gbbEcl.means[i] + stderr.gbbEcl[i])),
          lwd = 3,
          col = "black")  
  }
  i = i +1
}

```{r echo = F, include = T, warning=F}

##Running a Wilcoxon Rank Sum non parametric test for data that is not normally distributed

t.table = data.frame(Genotype1 = "WT(LoxP/cr)",
                     Genotype2 = "G85R(hr/cr)" ,
                     pval = wilcox.test(x = gbbEcl[gbbEcl$Genotype == "WT(LoxP/cr)","PercentEclosion"],
                                   y = gbbEcl[gbbEcl$Genotype == "G85R(hr/cr)","PercentEclosion"],
                                   paired = F)[[3]])

 t.temp = data.frame(Genotype1 = "G85R(hr/cr)",
                     Genotype2 = "OK371-gbb; G85R(hr/cr)",
                     pval = wilcox.test(x = gbbEcl[gbbEcl$Genotype == "G85R(hr/cr)","PercentEclosion"],
                                        y = gbbEcl[gbbEcl$Genotype == "OK371-gbb; G85R(hr/cr)","PercentEclosion"],
                                        paired = F)[[3]])
t.table = rbind(t.table, t.temp)

t.temp = data.frame(Genotype1 = "G85R(hr/cr)",
                    Genotype2 = "OK371-SaxA; G85R(hr/cr)",
                    pval = t.test(x = gbbEcl[gbbEcl$Genotype == "G85R(hr/cr)","PercentEclosion"],
                                       y = gbbEcl[gbbEcl$Genotype == "OK371-SaxA; G85R(hr/cr)","PercentEclosion"],
                                       paired = F)[[3]])
t.table = rbind(t.table, t.temp)

t.stripe = t.table$pval <= .05
#row.names(t.table) = c(1:nrow(t.table))

knitr::kable(t.table,
             caption = 'All t-tests for figure 1B eclosion data.')  %>%
kable_styling() %>%
row_spec(c(1:nrow(t.table))[t.table$pval <= .05], bold = T, color = "black", background = "gold")

temp = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/UBLegMorphologyData.csv")

temp$Genotype[temp$Genotype == "WT"] = "WT(cr)"
temp$Genotype[temp$Genotype == "G85R"] = "G85R(cr)"

temp$Genotype = factor(temp$Genotype, levels = unique(temp$Genotype))

morph.data = temp[,c(1:2,7:9,12:14)]

sum.morph = setNames(apply(morph.data[,3:8], MARGIN = 1, sum), morph.data$Genotype)

plot(x = NA,
     y = NA,
     type = 'n',
     ylim = c(0, 6),
     xlim = c(.5, 2.5),
     xaxt = "n",
     ylab= "Morphology Score",
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = "Leg Axon Morphology")

grid(nx=NA, ny=NULL, col = "grey50", lwd = .75)

boxplot(sum.morph~temp$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(0, 6),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = hex(std.colors[unique(temp$Genotype)], .25),
        add = T, 
        xaxt = "n",
        yaxt = "n",
        frame = F)

  axis(side = 1,
       at = c(1,2),
       lwd = 3,
       line = -.45,
       labels = unique(temp$Genotype),
       xpd = T)

    lines(x = c(0.4, 2.5),
       y = c(0,0),
       lwd = 3,
       xpd = T)

pval = t.test(x = sum.morph[1:9],
              y = sum.morph[10:18],
              paired = F)[[3]]

xpos = c(0, -.1, -.05, -.05, .1, -.2, .2, .05, .05,
         0, -.1, .1, -.2, 0, .2, -.05, .05, 0) + as.numeric(temp$Genotype)

points(x = xpos,
       y = sum.morph,
       cex = 2.25,
       pch = 21,
       bg= std.colors[temp$Genotype])

      axis(side = 2,
       at = c(0:6),
       lwd = 3,
       line = 0,
       labels = T,
       xpd = T,
       las = 2)

  text(x = 2.25,
       y = 5.75,
       label = paste0("pval = ", signif(pval, 3)))

### 2025-05-14 Shortcuts_OmicsQuickPlotFunctions.Rmd
update
updated files
Updated Russo Data
updated general data files for app
Russo Data update

ID = "gbb"

plot.G85R(ID)

@@

@@

metabID = 'NADH'

@@

gene.name = "gbb"

@@

heat.genes = c("dpp", "gbb", "put", "wit", "mav", "sax", "tkv", "repo", "ACC", "Ack-like")

@@

>>>>

ID = "Zw"

plot.G85R(ID)
G85R.FC[GeneIDKey[GeneIDKey$Symbol == ID, "FBgn"],]
G85R.FDR[GeneIDKey[GeneIDKey$Symbol == ID, "FBgn"],]

@@

ID = "FBgn0000635"

@@

metabID = "NADPH"

@@

gene.name = "Sod1"

@@

heat.genes = c("dpp", "gbb", "put", "wit", "mav", "sax", "tkv")

@@

heat.genes = c("gbb", "dpp", "wit", "Mad", "put", "sax", "tkv", "mav", "babo", "Smox")

serpe.heatmap.noman(heat.genes)
